{\tt APFELgrid}: a high performance tool for parton density determinations

### 2016-05-06 paper.tex
figure mods and ttbar references

We shall now examine the performance differences between
the two expressions for fast interpolated cross section prediction
Eq.~(\ref{eq:applconv}) ({\tt APPLgrid}) and Eq.~(\ref{eq:FK}) ({\tt
  FK}).
%
In order to provide a comprehensive benchmark, we consider here a wide range of
processes including LHC and Tevatron electroweak vector boson
production
measurements~\cite{Aaij:2012mda,Aaij:2012vn,Chatrchyan:2013mza,Chatrchyan:2013uja,Chatrchyan:2012xt,Aad:2013iua,Aad:2011fp,Aad:2011dm,Aaltonen:2010zza},
$t\bar{t}$ total
cross sections~\cite{ATLAS:2012aa,ATLAS:2011xha,TheATLAScollaboration:2013dja,Chatrchyan:2013faa,Chatrchyan:2012bra,Chatrchyan:2012ria},
double-differential Drell-Yan
cross sections~\cite{Chatrchyan:2013tia,CMS:2014jea} and inclusive jet
data~\cite{Chatrchyan:2012bja,Aad:2011fc,Aad:2013lpa,Abazov:2007jy}. Predictions
are performed over a wide range of kinematics, for a total of 52
source {\tt APPLgrid} files corresponding to the majority of available
LHC and Tevatron datasets of applicability to PDF determination.
While the source {\tt APPLgrid} files have varying grid densities in
$x$ and $Q^2$, for the purposes of comparison the corresponding {\tt
  FK} tables are produced consistently with 30 points in $x$, and at
an initial scale below the charm threshold, therefore with seven
active partonic species. These settings are chosen so as to provide a realistic
comparison, in a production environment the density and distribution of the
$x$-grid may be adjusted to match interpolation requirement.

>>>>

We shall now examine the performance differences between
the two expressions for fast interpolated cross section prediction
Eq.~(\ref{eq:applconv}) ({\tt APPLgrid}) and Eq.~(\ref{eq:FK}) ({\tt
  FK}).
%
In order to provide a comprehensive benchmark, we consider here a wide range of
processes including LHC and Tevatron electroweak vector boson
production
measurements~\cite{Aaij:2012mda,Aaij:2012vn,Chatrchyan:2013mza,Chatrchyan:2013uja,Chatrchyan:2012xt,Aad:2013iua,Aad:2011fp,Aad:2011dm,Aaltonen:2010zza},
$t\bar{t}$ total
cross sections~\cite{ATLAS:2012aa, Chatrchyan:2013faa,Chatrchyan:2012bra,Chatrchyan:2012ria},
double-differential Drell-Yan
cross sections~\cite{Chatrchyan:2013tia,CMS:2014jea} and inclusive jet
data~\cite{Chatrchyan:2012bja,Aad:2011fc,Aad:2013lpa,Abazov:2007jy}. Predictions
are performed over a wide range of kinematics, for a total of 52
source {\tt APPLgrid} files corresponding to the majority of available
LHC and Tevatron datasets of applicability to PDF determination.
While the source {\tt APPLgrid} files have varying grid densities in
$x$ and $Q^2$, for the purposes of comparison the corresponding {\tt
  FK} tables are produced consistently with 30 points in $x$, and at
an initial scale below the charm threshold, therefore with seven
active partonic species. These settings are chosen so as to provide a realistic
comparison, in a production environment the density and distribution of the
$x$-grid may be adjusted to match interpolation requirement.
